---
title: "ABA Assignment 2"
author: "Lee Bernstein"
date: "2024-03-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Part 1

1)
Linear relationship, multivariate normality, small or no multicollinearity, no auto correlations, Homoscedasticity

2) 
heart_disease = 15 - .2biking +.178smoking + E

Dependent Variable: heart_disease
Beta0/Y intercept: 15
Beta1/Slope coefficient: .2
X1/ Independent Variable: Biking
Beta2: .178
X2: smoking
E: Error

3)
sales = B0 + B1 * youtube + B2 * facebook + B3 * newspaper + Error

4)
```{r}
library(tidyverse)

df = read.csv("/Users/leebernstein/Downloads/Advanced BA/Data Files/DataFiles/Ice Cream Sales - temperatures.csv")
```

```{r}
#Summary Statistics 
#Two column names: Temperature, Ice Cream Profits
summary(df)
```

```{r}
#No missing values
sum(is.na(df))
```

```{r}
#365 Rows, 2 Columns
dim(df)
```

```{r}
#Data Type
class(df$Temperature)
class(df$Ice.Cream.Profits)
```

```{r}
#There seems to be a correlation between higher temperatures having increased profit
plot(df)
```

```{r}
#Partitioning the data
library(caret)

#Set seed for reproducibility
set.seed(1234)

#Creating data partition into 70% training and 30% testing
index = createDataPartition(df$Temperature, p=.7, list = FALSE)

#Creating the training and testing data
train_data <- df[index, ]
test_data  <- df[-index, ]
```

```{r}
ctrl <- trainControl(method = "cv", number = 5)
model_train = train( df$Temperature~ ., data = train_data, method = "lm", trControl = ctrl)
```

```{r}
pred_test = predict(ml_model, newdata = test_data)
```

I think that this dataset fits better into a simple regression model rather than a multi one. Due to the fact that there are only two variables, with one being the dependant variable








