---
title: 'Assignment 0: Data Basics and GitHub'
author: "Lee Bernstein"
date: "2024-01-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("ggplot2")
library(ggplot2)
```

```{r}
loans = read.csv("/Users/leebernstein/Downloads/Advanced BA/Data Files/loan_default_data_set.csv")
loans
```

Question 1

There are 21 different columns with 20,000 rows, you can run many different kinds of models, including correlation plots, regression, and predictive models depending on what you are looking for

Question 2 

The two columns that interest me are rep_income and rep_education, I believe that there could be a high correlation between the two

Question 3

There are a few different kinds of data types including, doubles (dbl), integers (int), and characters (chr)

Question 4

There are some missing values in the pct_card_over_50_uti column

Question 5

Data Visualization

```{r}
boxplot(loans$rep_income)
```

Question 6

Summary Statistics
```{r}
summary(loans$rep_income)
```








