---
title: "Assignment 4 - Time Series and Forecasting"
author: "Lee Bernstein"
date: "2024-04-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

sales = readxl::read_xlsx("/Users/leebernstein/Downloads/Advanced BA/Data Files/DataFiles/Sales.xlsx")
vintage = readxl::read_xlsx("/Users/leebernstein/Downloads/Advanced BA/Data Files/DataFiles/Vintage.xlsx")

library(tseries)
library(forecast)
library(dplyr)
library(zoo)
library(Metrics)
library(ggplot2)
library(reshape2)
```


Part 1: Sales

```{r}
#Sorting data
sales = sales[order(as.Date(sales$Week, format="%m%d%Y")),]
sales
```

```{r}
#Create moving averages
sales_wk3 = rollapply(sales$Sales, width = 3, FUN = mean)
sales_wk4 = rollapply(sales$Sales, width = 4, FUN = mean)
sales_wk5 = rollapply(sales$Sales, width = 5, FUN = mean)

print("Moving Average 3 Weeks:")
print(sales_wk3)
print("Moving Average 4 Weeks:")
sales_wk4
print("Moving Average 5 Weeks:")
sales_wk5
```
```{r}
#Exponential Smoothing
exp_smooth = forecast(sales_wk3, h = , method = "ets", alpha =.5)
```

```{r}
sales = data.frame(sales)
```

```{r}
dim_data = dim(sales)
dim_data
```

```{r}
#Splitting Data
len_train = ceiling((.7*dim_data[1]))
len_train
```

```{r}

training_set = sales$Sales[1:len_train]
test_set = sales$Sales[(len_train+1):dim_data[1]]
```

```{r}
#Training Set plot
plot(training_set, type="l", xlab = "Number of Weeks", ylab="Number of Sales")
```

```{r}
#Original Plotted Data
plot(sales$Sales, type="l", xlab = "Weeks", ylab="Number of Sales")
```

```{r}
#Stationary Test
kpss.test(training_set)
adf.test(training_set)
```

```{r}
#Determining AR needed
pacf(training_set)
```

```{r}
#Determine MA needed
acf(training_set)
```

```{r}
#ARIMA Model
AutoArimaModel = auto.arima(training_set)
AutoArimaModel
```

```{r}
#Creating Forecast
forecast = predict(arimaModel, (dim(data.frame(test_set))[1]))
```

```{r}
#Accuracy Testing
rmse(test_set, forecast$pred)
mae(test_set, forecast$pred)
mse(test_set, forecast$pred)
mape(test_set, forecast$pred)
```

From testing the different accuracies, the model that shows the best is MAPE, since it's value is closest to 0


Part 2: Case Study

```{r}
summary(vintage)
```


```{r}
#Original Plot Data
plot(vintage$Sales, type="l", xlab = "Months", ylab="Number of Sales")
```
By looking at the original data plot, there seems to be seasonality, with the highest sales in first 3 months 


Creating a forecast for fourth year sales
```{r}
vintage$Month = as.Date(vintage$Month)
```

```{r}
#Dummy Variables
vintage$Month = factor(months(vintage$Month), levels = month.name)
dummies = model.matrix(~ Month - 1, data = vintage)
```

```{r}
model_data = cbind(vintage, dummies)
```

```{r}
#Regression Model
model = lm(vintage$Sales ~ dummies, data = model_data)
```

```{r}
#Data Frame Creation
fourth_year = seq(as.Date("2024-01-01"), by = "month", length.out=12)
fourth_year_month = factor(months(fourth_year), levels = levels(vintage$Month))
fourth_year_dummies = model.matrix(~ fourth_year_month -1)
```

```{r}
#Turning dummy into Data Frame
fourth_year_data = data.frame(dummies = fourth_year_dummies)
```

```{r}
fourth_year_forecast = predict(model, newdata = fourth_year_data)
print(fourth_year_forecast)
```
From this model we create dummy variables that pose as new months for a 4th year. We then take those months and combine it into the data set to predict and forecast future sales.Assuming that that January sales for the 4th year are $295,000, this model has a large forecast error. To resolve uncertainty from the model, more fine tuning and a stronger model can be made.  




